\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage[framemethod=tikz]{mdframed}
\usepackage[style=apa]{biblatex}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{array}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={GEOG342},
    pdfpagemode=FullScreen,
    }

\setlength{\parindent}{0pt}



\begin{document}

\title{342 Presentation Contributions}
\author{Sophie Kolston}
\date{}

\maketitle


You can view our video \href{https://www.youtube.com/watch?v=tiYgL51dHy0&t=1s}{here} (\url{https://www.youtube.com/watch?v=tiYgL51dHy0&t=1s}) \\

All members of the team worked well to complete the presentation. We communicated in a team, contributed to a script and presentation slideshow then recorded the video and uploaded for submission. All members of the team did their part well and gave feedback on every stage of the process. We scheduled zoom calls and had a group chat for communication which ended up working well and I had no issues with any other member of the group. Specifically, in terms of who did what: \\

I, Sophie Kolston, organized the zoom calls, wrote my own section and helped proof read everyone elses section. I also wrote the introduction section \\

Jaxon wrote the comparisons section, on top of the general group contributions of writing their section of the script and presenting their slide. \\

Josh wrote their section as well as helping out Jaxon with the comparison section. \\

Ben wrote the comparisons section as well as their own section. Ben also wore a suit to the recording, which is surely worth a lot in terms of contributions. I tried to match this level of professionalism with a shirt but it was clearly not the same. \\

Cody wrote the outro as well as his own section. He also did the comparisons slides and cleaned up all of the slides in general.\\

If it wasn't mentioned specifically, every member of the team collaborated to edit the section, timing and slideshow. Again, everyone contributed well. 




\end{document}